Silent pessimists - researchers' perceptions of malaria eradication and implications for health spending

### 2017-10-11 paper.Rmd
big update

bibliography: library.bib
params:
  get_new_data: False
output: rticles::elsevier_article
---

@@

# Get data
source('prepare_data.R')
```

@@

```{r, results = 'markup'}
# stargazer(ols1, heck1, ml1,
#           header = FALSE,
#           # se=list(cse(ols1),NULL,NULL),
#           title="Regression on years until eradication", 
#           type="text",
#           df=FALSE, digits=4)
# # summary(ols1)
# # summary(heck1)

@@

ggplot(data = results) + 
  geom_violin(aes(x = bb,
           y = ranking),
           fill = 'orange',
              alpha = 0.6) +
  geom_jitter(aes(x = bb,
           y = ranking),
           color = 'black',
           with = 0.4,
           height = 0.4,
              alpha = 0.3,
              size = 1) +
  theme_publication(base_size = 10) +
  labs(x = 'WHO Building block',
       y = 'Ranking',
       title = 'Perceived areas needing attention',
       subtitle = 'Small points: jittered individual responses; large triangles: averages') +
  geom_point(data = results_agg,
             aes(x = bb,
                 y = avg),
             size = 5,
             pch = 17,
             color = 'black',
             alpha = 0.8) +
  ylim(0, 6)
ggsave('~/Desktop/figure2.png', height = 4, width = 5.5)
```

>>>>

bibliography: library.bib
params:
  get_new_data: False
output: rticles::elsevier_article
preprint: false
---

@@

# Get data
source('prepare_data.R', echo = FALSE)
```

@@

```{r, results = 'markup'}

ggplot(data = heckman,
       aes(x = years,
           y = value,
           color = key,
           lty = key)) +
  geom_line(alpha = 0.8) +
  geom_point(alpha = 0.6) +
  theme_black() +
  labs(x = 'Years',
       y = 'Likelihood of eradication') +
  scale_linetype_manual(name = '', values = 1:2) +
  scale_color_manual(name = '', values = c('white', 'darkorange')) +
  labs(title = 'Heckman selection adjustment')

@@

library(ggridges)
ggplot(data = results %>% filter(!is.na(ranking)),
       aes(x = ranking,
           y = bb,
           fill = bb)) +
  geom_density_ridges(#fill = 'darkorange',
                      alpha = 0.6,
                      scale = 1.5) +
  theme_black() +
  xlim(0,30) +
  labs(x = 'Perceived importance',
       y = 'WHO Building Block') +
 scale_fill_cyclical(values = c("darkorange", "yellow"))

# ggplot(data = results) + 
#   geom_violin(aes(x = bb,
#            y = ranking),
#            fill = 'orange',
#               alpha = 0.6) +
#   geom_jitter(aes(x = bb,
#            y = ranking),
#            color = 'black',
#            with = 0.4,
#            height = 0.4,
#               alpha = 0.3,
#               size = 1) +
#   theme_publication(base_size = 10) +
#   labs(x = 'WHO Building block',
#        y = 'Ranking',
#        title = 'Perceived areas needing attention',
#        subtitle = 'Small points: jittered individual responses; large triangles: averages') +
#   geom_point(data = results_agg,
#              aes(x = bb,
#                  y = avg),
#              size = 5,
#              pch = 17,
#              color = 'black',
#              alpha = 0.8) +
#   ylim(0, 6)
```
